Coherent optical association of a single molecule

### 2020-10-15 paper.tex
Update on Overleaf.

\documentclass[aps,prl,twocolumn,superscriptaddress]{revtex4-1}
% \documentclass[aps,twocolumn,secnumarabic,balancelastpage,amsmath,amssymb,nofootinbib]{revtex4-1}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsfonts}
\usepackage{color}
\usepackage{graphics}
\usepackage[pdftex]{graphicx}
\usepackage[utf8x]{inputenc}
\usepackage[colorlinks=true]{hyperref}

@@

\begin{document}
\title{Coherent optical association of a single molecule}
\author{Yichao Yu}
\email{yichaoyu@g.harvard.edu}
\cuaphysics
\author{Kenneth Wang}
\cuaphysics
\author{Jonathan~D.~Hood}
\affiliation{Department of Chemistry, Purdue University, West Lafayette, Indianna, 47906}
\author{Lewis~R.~B.~Picard}
\cuaphysics
\author{Jessie~T.~Zhang}
\cuaphysics
\author{William~B.~Cairncross}
\cuaphysics
\author{Jeremy~M.~Hutson}
\affiliation{Joint Quantum Centre Durham-Newcastle, Department of Chemistry, Durham University, Durham, DH1 3LE, United Kingdom}
\author{Till Rosenband}
\author{Kang-Kuen~Ni}
\email{ni@chemistry.harvard.edu}
\affiliation{Department of Chemistry and Chemical Biology, Harvard University, Cambridge, Massachusetts 02138, USA}
\affiliation{Department of Physics, Harvard University, Cambridge, Massachusetts 02138, USA}
\affiliation{Harvard-MIT Center for Ultracold Atoms, Cambridge, Massachusetts 02138, USA}

@@

Here, we demonstrate coherent association of an atom pair to a weakly bound molecule using a two-photon optical Raman transfer via an electronic excited state, without the use of a Feshbach resonance nor a narrow excited state, schematically shown in Fig.~\ref{f-theory}A. The resulting single molecule is in a single internal quantum state and predominately in its motional ground state.  Our scheme is based on using a theoretically determined vibrational state of the electronic excited state $c^3\Sigma^+$ that has the best raman Rabi frequency to photon scattering ratio. To further increase this ratio and reduce technical requirements such as intensity stability, we choose an initial and final state where the matrix elements with the excited state are as balanced as possible. This approach minimizes the reliance on system specific properties and could therefore be applied to creating other molecular species or larger molecules atom-by-atom with full quantum state control.
% (also this result represents full quantum-state control of single [neutral] molecules, the second time ever (first being our NaCs Feshbach molecules))

@@

The essence of an optical Raman transfer can be illustrated using a three-level system (Fig.~\ref{f-theory}A), where the initial atomic state, the target weakly-bound molecular state are coupled to an excited intermediate state by two photons, $\Omega_a$ and $\Omega_m$, with single photon detuning $ \Delta $, and two photon detuning, $ \delta$.  %(Ultimately, we calculate with contribution of all vibrational states of the excited electronic potential, $c^3\Sigma^+$)
The transfer Raman Rabi Rate is $ \Omega_a\Omega_m / 2\Delta$ accompanied by a photon scattering rate of $\Gamma_e \Omega^2 / 4\Delta^2$...(sum of i terms\textcolor{red}{KW: I was intending to only mention the sum over terms at the end when we exit the 3 level system.})\textcolor{blue}{check factor of 2. KW: The 2 in the denominator is including cross coupling. 4 without cross coupling. Since cross coupling is mentioned later, maybe leave this with 4?}, where $ \Gamma_e $ is the excited state linewidth~\cite{Wineland2003}. %, depends on both of these matrix elements and the single photon detuning~\cite{Wineland2003}.
Unlike for Raman transitions in atoms, the two matrix elements here, $ \Omega_m$ and $ \Omega_a$, are greatly imbalanced %. Since $ \Omega_m $ is generally much larger than $ \Omega_a $
due to the small wavefunction overlap between the atomic state and the excited molecular state. The scattering rate therefore predominantly comes from the molecular state, $ \Gamma_e \Omega_m^2 / 2\Delta^2$, where $ \Gamma_e $ is the excited state linewidth. \textcolor{blue}{(blue text can potentially be moved to footnote) Furthermore, because the energy difference of the atomic and the weakly bound states are small ($<$1~GHz) comparing to $\Delta$, the power of the Raman beams are chosen to be equal to gives the largest Raman Rabi rate at a fixed total power. %There is
  An additional factor of 2 is included in the scattering rate because the molecular state scatters off of both Raman beams at roughly the same single photon detuning. } Thus, the ratio between the Raman Rabi frequency and the scattering rate, $ \Omega_a/\Omega_m \times \Delta/\Gamma_e $, depends on the ratio of the two matrix elements and how far detuned the laser is from the transition in units of the linewidth. To ensure a coherent process, larger detuning is preferred while achieving a realistic Raman Rabi frequency. %However, the detuning cannot be too large, since that will reduce the Raman Rabi frequency.
With the multiple excited vibrational states present in a molecular potential, the total scattering rates and Rabi rates become a sum of the scattering rates and Rabi rates over all the states. %There are also many possible intermediate states to choose from.

Pioneering experiments used weakly bound molecular excited states in the Raman transition to ensure a large Raman Rabi frequency~\cite{Wynar2000,Rom2004}. However, such choice of state suffers from strong scattering of the nearby atomic excited state to render it incoherent, resulting in molecule loss. The scattering  is  proportional to $1/\delta_{thresh}^2$, where $\delta_{thresh}$ is the detuning from the dissociation threshold, and thus can  be made smaller by detuning away from the dissociation threshold.

@@

To find the optimal excited intermediate state, we perform a  calculation of the Raman Rabi frequency and scattering rate at different detunings from the atomic threshold taking into account of all states of the $c^3\Sigma$ excited molecular state potential (full result in SM)~\cite{Liu2017} \textcolor{red}{KW: I have only done the calculations with c3Sigma only, cause the b3Pi is highly spin orbit coupled, and not necessarily trustworthy where we are. I can also include a citation to the paper with that potential?}. As shown in Fig.~\ref{f-theory}B, the ratio of the Raman Rabi rate to scattering rate can be made larger for more deeply bound states compared to weakly bound states at a cost of a smaller Raman Rabi frequency.  %Since for a typical molecular potential the spacing between states
% decreases with increasing vibrational levels,
% a weakly bound excited molecular state
% This further increases the scattering rate for a weakly bond excited state.
% Based on these considerations, % a weakly bound excited molecular state may not be the best choice for the intermediate state in the Raman transfer. Thus,
% we calculated both the Raman Rabi frequency and the scattering rate at different detunings (full result is shown in SM). As seen in Fig.~\ref{f-theory}B,
% we found a distinct optimal regime from what has been explored experimentally previously.
% Namely, despite a smaller Raman Rabi frequency at deeply bound intermediate states, the Rabi frequency to scattering rate ratio is much higher as compared to a weakly bound intermediate state.
As a result, we choose a deeply bound molecular excited state ($v'=0$ of $c^3\Sigma^+$) as an intermediate state to drive the Raman transition. %(mention the trend, also v'=12 will work as similarly as v'=0)

@@

As previously discussed, the ratio of the Raman Rabi rate to the scattering rate is proportional to the $ \Omega_a/\Omega_m $ ratio. The smaller this ratio is, the farther the laser needs to be detuned to achieve the same Raman Rabi rate to scattering rate ratio, which lowers the Raman Rabi rate. In addition to reducing how far the laser needs to be detuned from the transition, a larger $ \Omega_a/\Omega_m$ ratio also relaxes the intensity stability requirement, a key potential technical limitation. The position of the resonance depends on the laser power predominantly through the AC Stark shift on the molecular state, $ \Omega_m^2 / 2\Delta $. \textcolor{red}{KW: Can also include similar footnote here about cross coupling? The 2 in the denominator is assuming cross coupling and equal powers.} The ratio of the AC Stark shift to the Raman Rabi frequency is $ \Omega_m / \Omega_a $, Thus, the laser intensity needs to be stabilized to better than the inverse of this ratio to fluctuate by less than a linewidth in a coherent process. The ratio, $ \Omega_a/\Omega_m $ can be changed through the choice of initial and final states. In particular, it can be made larger by increasing the coupling of the atomic state with the excited molecular state. Due to the small size of the molecular wavefunction, the coupling between the ground atomic state and the excited molecular state is approximately proportional to the value of the relative atomic wavefunction at short distance within the molecular potential. In addition to the confinement, this value is related to the interaction between the two atoms. For states with a large scattering length (positive or negative), the phase shift in the relative wavefunction between the atoms can significantly increase the short range wavefunction (Fig.~\ref{f-theory}C). The increase in the coupling is proportional to (quote/cite Olive's equation?). For our system, among the stable spin combinations, 4422 and 3311 both have small scattering lengths of $ a_{4422}= 30.4a_0, a_{3311} = 13.7a_0 $ respectively, but the 3332 combination has a large and negative scattering length of $ a_{3322} = -693.8a_0 $ (interaction shift $\approx$ binding?)~\cite{Hood2019}. In addition to the increased atomic coupling, $ \Omega_a $, with the 3322 hyperfine combination, coupled channel calculations show that the most weakly bound molecular state that is predominantly in the 3322 spin combination also has reduced coupling, $ \Omega_m $, with the excited state when compared with the 4422 and 3311 bound states. Therefore, using an initial 3322 hyperfine combination results in a $ \Omega_a/\Omega_m$ ratio of about 0.05 instead of a ratio of about 0.003 with the 4422 or 3311 combinations.

@@

Thus, we choose the 3322 spin combination as our initial state and drive to the first bound state for the 3322 spin combination. (We might want to mention that those ratios are for 80 kHz spherical trap if we want to give more details about the coupled channel calculation anywhere...)

@@

%% Preparation
To perform the Raman transfer, we use our apparatus described in our previous work~\cite{Liu2019}. Our experiment begins by stochastically loading a single ${}^{23}\mathrm{Na}$ atom and a single ${}^{133}\mathrm{Cs}$ atom into an optical tweezer from a dual-species MOT\todo{cite na loading paper} into separate optical tweezers. The atoms are initially imaged to distinguish between loading of two atoms, one atom (Na or Cs), or no atom in order to perform post selection. We then perform simultaneous Raman sideband cooling (RSC) to cool both atoms into the 3-dimensional motional ground state of their optical tweezers. After RSC, the Na tweezer is moved by sweeping the frequency on an acoustical optical beam deflector (AOBD) to overlap with the Cs tweezer before smoothly ramping off, so that the Na and Cs atoms are merged into the same tweezer~\cite{Liu2019}. The spin states for the Na and Cs atoms after RSC and during the merge process are $|F=2,m_F=2\rangle_{Na}$ and $|F=4,m_F=4\rangle_{Cs}$ respectively. This states combination has a low scattering length, which allows the two atoms to be merged into the same tweezer with minimum pertubation on each other and thus they remain in the motional ground state after the merge.

After preparing the Na and Cs atoms in the same tweezer in a single quantum state, we need to drive the atoms into the large scattering length 3322 hyperfine combination. To do this, we perform a spin flip taking into account the interaction shift~\cite{Hood2019} using a Cs Raman transition to drive the Cs atom into the $|F=3,m_F=3\rangle_{Cs}$ state. The new spin state combination has a larger scattering length of $-693.8 a_0$ which generates a interaction shift of $-30.7 kHz$ in the tweezer. This interaction shift is larger than the differential axial trapping frequency between Na and Cs atoms, which decouples the relative and center of mass motional state and improves the robustness of our preparation of the relative motion ground state.

@@

%% Transfer scheme
After the atoms are prepared in the 3322 hyperfine combination, we then perform the Raman transfer. The pulse sequence for this step is shown in Fig.~\ref{f-raman}B. Instead of adding another beam to drive the Raman transition on the atoms in the tweezer, we use the tweezer itself to achieve this goal. In particular, we turn on two co-propagating frequencies in the tweezer during the Raman pulse. The dual use of the tweezer beam ensures that there is not any undesired laser frequency that can interfere with the Raman transition, and also allows us to maximize the Raman Rabi frequency and minimize the transfer time. After the total tweezer power is set to the desired value, we smoothly ramp down the power of one frequency in the tweezer while simultaneously ramping up the power of a different frequency so that the total tweezer power remains unchanged. Both frequencies are kept on for a variable length of time before the process is reversed and we return to having a single frequency in the tweezer.
In additional to reducing the number of laser beams during the Raman transition,
we also found the spectral purity of the laser to be critical for achieving a higher
transfer efficiency. The tweezer and Raman beams are generated by amplifying a $1037 \mathrm{nm}$
external cavity diode laser (ECDL) with a Raman fiber amplifier,
which produces a broad band amplified spontaneous emission (ASE),
in addtional to the desired frequency, and increases the scattering rate due to coupline to
other excited states.
We use a bragg grating with a line width (FWHM) of $50 \mathrm{GHz}$ to clean up the
laser spectrum and found it reduces the scattering rate by at least a factor of $2$
for certain tweezer detuning.

@@

The ratio of molecule scattering rate to the Rabi frequency is larger than the theory prediction
by more than a factor of $10$.
Based on the calculation above, if this comes from the coupling to the $v'=0$ excited state,
it can be either due to a high ratio of $\Omega_m / \Omega_a$ or a large $\Gamma_e$.
Additionally, coupling to other excited states can also adds an offset to both the Raman
Rabi frequency and the scattering rate which can affect the scattering rate
to Rabi frequency ratio.

@@

First we look at the change in resonance frequency.
As a function of the tweezer power, we observe a linear dependency on the resonance frequency
caused by the differential light shift between the atomic and molecular state (Fig.~\ref{f-det}A).
When we vary the tweezer frequency around the $v'=0$ excited state,
we can further observe a $1/\delta$ component and a constant component
in the experimentally explored region.
The background is caused by coupling to other excited states that are further away in energy.
The $1/\delta$ component, however, is predominantly due to the coupling between
the molecular state and the $v'=0$ excited state.
From this measurement, we can calculate a matrix element between the molecular state and
the excited state, $\Omega_m$, of $2\pi\times36.162(20) \mathrm{MHz}/\sqrt{\mathrm{mW}}$
or $2\pi\times140.056(78) \mathrm{MHz}$ for the $15 \mathrm{mW}$ tweezer power used above.
This number is consistent with the value of
$2\pi\times27 \mathrm{MHz}/\sqrt{\mathrm{mW}}$ \todo{ref/sm theory}.
\todo{make sure theory part mentions $\Omega_{down}\gg\Omega_{up}$,
  also $\Omega$ vs $\Omega'$ for the single leg vs cross coupling number.}

In order to calculate the matrix element ratio,
next we discuss the dependencies of the Raman Rabi frequency.
The Raman Rabi frequency shows a non-linear dependency on the tweezer power due to the change
in the atomic wavefunction caused by the change in confinement (Fig.~\ref{f-det}B).
The atomic matrix element, $\Omega_a$,
is proportional to the the short range atomic wavefunction amplitude,
which scales as $P^{0.375}$ for weakly interacting particles.
However, due to the strong interaction between the two atoms, this approximation breaks down.
Instead, theory calculation shows that the scaling is very well approximated by $P^{0.29}$
within the range of confinement in our experiment.
Combined with the intensity factor, the Raman Rabi frequency should scale with $P^{1.29}$,
which agrees with our experimental result.
Similar to the light shift, there is also an offset and
a $v'=0$ component in the Raman Rabi frequency.
The $v'=0$ component of the Raman Rabi frequency is
$2\pi\times161.8(22) \mathrm{Hz\cdot mW^{-1.29}}$,
or $2\pi5.324(73)\mathrm{kHz}$ at $15 \mathrm{mW}$ tweezer power.
Together with the $\Omega_m$ measured above, the up leg Rabi frequency is
$2\pi11.53(16)\mathrm{MHz}$.
This gives a Rabi frequency, and therefore matrix element, ratio of $12.14(16)$,
which is in fact better than the theory prediction of $23.7$
and should not cause the scattering from the $v'=0$ state to be higher than expected.

Unfortunately, the offset in the Raman Rabi frequency fit cancels
the Rabi frequency for red detuning Raman transition and reduces it by about $30\%$
at the current detuning. However, this difference is not enough to explain
the difference we observed in the experiment.
The same offset will increase the Rabi frequency for blue detuning
but we have observed additional excited states at slightly higher frequencies
which prevent the blue side of the transition to be usuable for Raman transition.

\begin{figure*}
  \includegraphics[height=4.5cm]{fig4.pdf}
  \caption{Raman transition parameters as a function of tweezer and Raman power and detuning.
    (A) The light shift of the Raman resonance scales as $P_{tweezer}$
    and follows $1/\delta$ with an offset.
    The fit also includes a small term that is proportional to $P_{tweezer}^2$
    which is caused by the effective magnetic field generated by the tweezer which is
    perpendicular to the real magnetic field.
    (B) Raman Rabi frequency scales as $P_{tweezer}^{1.29}$ and follows $1/\delta$ with an offset.
    From these results we can confirm the theory prediction of
    the atom-molecule matrix element ratio.
    (C) Atomic scattering rate scales as $P_{tweezer}^{2.58}$,
    this is consistent with a two photon scattering process.
    We have not measured a clear dependency of the loss rate on the tweezer detuning.
    \label{f-det}}
\end{figure*}

Based on our previous measurements of the excited state using photoassociation (PA) spectroscopy,
the linewidth of the $v'=0$ excited state is no larger than $20 \mathrm{MHz}$.
This suggests that the excited state linewidth should not cause a stronger than expected
scattering from $v'=0$ state either.

>>>>

\documentclass[aps,prl,twocolumn,superscriptaddress]{revtex4-1}
% \documentclass[aps,twocolumn,secnumarabic,balancelastpage,amsmath,amssymb,nofootinbib]{revtex4-1}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsfonts}
\usepackage{color}
\usepackage{graphics}
\usepackage[pdftex]{graphicx}
\usepackage[utf8x]{inputenc}
\usepackage[colorlinks=true]{hyperref}
\usepackage{footmisc}
\usepackage{braket}

@@

\begin{document}
\title{Coherent optical association of a single molecule}
\author{Yichao Yu}
\email{yichaoyu@g.harvard.edu}
\cuaphysics
\author{Kenneth Wang}
\cuaphysics
\author{Jonathan~D.~Hood}
\affiliation{Department of Chemistry, Purdue University, West Lafayette, Indianna, 47906}
\author{Lewis~R.~B.~Picard}
\cuaphysics
\author{Jessie~T.~Zhang}
\cuaphysics
\author{William~B.~Cairncross}
\cuaphysics
\author{Jeremy~M.~Hutson}
\affiliation{Joint Quantum Centre Durham-Newcastle, Department of Chemistry, Durham University, Durham, DH1 3LE, United Kingdom}
\author{Till Rosenband}
\cuaphysics
\author{Kang-Kuen~Ni}
\email{ni@chemistry.harvard.edu}
\cuaphysics
%\affiliation{Department of Chemistry and Chemical Biology, Harvard University, Cambridge, Massachusetts 02138, USA}
%\affiliation{Department of Physics, Harvard University, Cambridge, Massachusetts 02138, USA}
%\affiliation{Harvard-MIT Center for Ultracold Atoms, Cambridge, Massachusetts 02138, USA}

@@

Here, we demonstrate coherent association of an atom pair to a weakly bound molecule using a two-photon optical Raman transfer via an electronic excited state, schematically shown in Fig.~\ref{f-theory}A, neither using a Feshbach resonance nor a narrow excited state. The resulting single molecule is in a single internal quantum state and predominately in its motional ground state.  Our scheme is based on a choice of vibrational state of the electronic excited state $c^3\Sigma^+(\Omega = 1)$ that has the theoretical best raman Rabi frequency to photon scattering ratio. To further increase this ratio and reduce technical requirements such as intensity stability, we choose an initial and final state where the matrix elements with the excited state are as balanced as possible. This approach minimizes the reliance on system specific properties and could therefore be applied to creating other molecular species or larger molecules atom-by-atom with full quantum state control.
% (also this result represents full quantum-state control of single [neutral] molecules, the second time ever (first being our NaCs Feshbach molecules))

@@

The essence of an optical Raman transfer can be illustrated using a three-level system (Fig.~\ref{f-theory}A), where the initial atomic state, the target weakly-bound molecular state are coupled to an excited intermediate state by two photons, $\Omega_a$ and $\Omega_m$, with single photon detuning $ \Delta $, and two photon detuning, $ \delta$.  %(Ultimately, we calculate with contribution of all vibrational states of the excited electronic potential, $c^3\Sigma^+$)
The transfer Raman Rabi Rate, $ \Omega_a\Omega_m / 2\Delta$, is accompanied by a photon scattering rate which is a sum of all coupling sources %of $\sum_{n=i} \Gamma_e \Omega_i^2 / 4\Delta^2 $,
$\Gamma_e \Omega^2 / 4\Delta^2 $, where $ \Gamma_e $ is the excited state linewidth~\cite{Wineland2003}. %, depends on both of these matrix elements and the single photon detuning~\cite{Wineland2003}.
Unlike for Raman transitions in atoms, the two matrix elements here, $ \Omega_m$ and $ \Omega_a$, are greatly imbalanced %. Since $ \Omega_m $ is generally much larger than $ \Omega_a $
due to the small wavefunction overlap between the atomic state and the excited molecular state, and the scattering is predominantly from the molecular state. Furthermore, the energy difference between the atomic and weakly bound state is small ($ < 1 \mathrm{GHz} $) compared to the single photon detuning, $ \Delta $, so the molecular state can scatter off both beams at roughly the same single photon detuning. Thus, the scattering is given by $ \Gamma_e \Omega_m^2 / 2\Delta^2$ \footnote{We choose the two beams to have equal power, which gives the highest Raman Rabi Rate at a fixed total power. Thus, this results in an additional factor of 2 coming from scattering off 2 beams.}.
The ratio between the Raman Rabi frequency and the scattering rate, $ \Omega_a/\Omega_m \times \Delta/\Gamma_e $, depends on the ratio of the two matrix elements and how far detuned the laser is from the transition in units of the linewidth. To ensure a coherent process, a detuning as large as possible, while maintaining a realistic Raman Rabi frequency, is preferred. %However, the detuning cannot be too large, since that will reduce the Raman Rabi frequency.
With the multiple excited vibrational states present in a molecular potential, the total scattering rate and Raman Rabi rate become a sum over the scattering rates and Raman Rabi rates of the individual states. %There are also many possible intermediate states to choose from.

Pioneering experiments used weakly bound molecular excited states in the Raman transition to ensure a large Raman Rabi frequency~\cite{Wynar2000,Rom2004}. However, such choice of state suffers from strong scattering of the nearby atomic excited state to render it incoherent, resulting in molecule loss. This scattering is  proportional to $1/\delta_{thresh}^2$, where $\delta_{thresh}$ is the detuning from the dissociation threshold, and thus can  be made smaller by detuning away from the dissociation threshold.

@@

To find the optimal excited intermediate state, we perform a  calculation of the Raman Rabi frequency and scattering rate at different detunings from the atomic threshold taking into account of all states of the $c^3\Sigma^+(\Omega = 1)$ excited molecular state potential (full result in SM)~\cite{Liu2017, Grochola2011}. As shown in Fig.~\ref{f-theory}B, the ratio of the Raman Rabi rate to scattering rate can be made larger for more deeply bound states compared to weakly bound states at a cost of a smaller Raman Rabi frequency.  %Since for a typical molecular potential the spacing between states
% decreases with increasing vibrational levels,
% a weakly bound excited molecular state
% This further increases the scattering rate for a weakly bond excited state.
% Based on these considerations, % a weakly bound excited molecular state may not be the best choice for the intermediate state in the Raman transfer. Thus,
% we calculated both the Raman Rabi frequency and the scattering rate at different detunings (full result is shown in SM). As seen in Fig.~\ref{f-theory}B,
% we found a distinct optimal regime from what has been explored experimentally previously.
% Namely, despite a smaller Raman Rabi frequency at deeply bound intermediate states, the Rabi frequency to scattering rate ratio is much higher as compared to a weakly bound intermediate state.
As a result, we choose a deeply bound molecular excited state ($v'=0$ of $c^3\Sigma^+(\Omega = 1)$) as an intermediate state to drive the Raman transition. %(mention the trend, also v'=12 will work as similarly as v'=0)

@@

As previously discussed, the ratio of the Raman Rabi rate to the scattering rate is proportional to the $ \Omega_a/\Omega_m $ ratio. The smaller this ratio is, the farther the laser needs to be detuned to achieve the same Raman Rabi rate to scattering rate ratio, which lowers the Raman Rabi rate. In addition to reducing how far the laser needs to be detuned from the transition, a larger $ \Omega_a/\Omega_m$ ratio also relaxes the intensity stability requirement, a key potential technical limitation. The position of the two photon resonance depends on the laser power predominantly through the AC Stark shift on the molecular state, $ \Omega_m^2 / 2\Delta $ \footnote{There is an additional factor of 2 to account for the Stark shift of both beams.}. The ratio of the AC Stark shift to the Raman Rabi frequency is $ \Omega_m / \Omega_a $, Thus, the laser intensity needs to be stabilized to better than the inverse of this ratio to fluctuate by less than a linewidth in a coherent process. The ratio, $ \Omega_a/\Omega_m $ can be changed through the choice of initial and final states. In particular, it can be made larger by increasing the coupling of the atomic state with the excited molecular state. Due to the small size of the molecular wavefunction, the coupling between the ground atomic state and the excited molecular state is approximately proportional to the value of the relative atomic wavefunction at short distance within the molecular potential. In addition to the confinement, this value is related to the interaction between the two atoms. For states with a large scattering length (positive or negative), the phase shift in the relative wavefunction between the atoms can significantly increase the short range wavefunction (Fig.~\ref{f-theory}C). The increase in the coupling is proportional to (quote/cite Olive's equation?). For our system, we denote the possible hyperfine states of the atoms as $ \ket{\uparrow_{\text{Cs}}} = \ket{F=4,m_F=4}_{\text{Cs}}, \ket{\downarrow_{\text{Cs}}} = \ket{F=3,m_F=3}_{\text{Cs}}, \ket{\uparrow_{\text{Na}}} = \ket{F=2,m_F=2}_{\text{Na}}, $ and $ \ket{\downarrow_{\text{Na}}} = \ket{F=1,m_F=1}_{\text{Na}}$. Among the stable spin combinations, $\ket{\uparrow_{\text{Na}}\uparrow_{\text{Cs}}}$ and $\ket{\downarrow_{\text{Na}}\downarrow_{\text{Cs}}} $ both have small scattering lengths of $ 30.4a_0 $, and $ 13.7a_0 $ respectively, but the $\ket{\uparrow_{\text{Na}} \downarrow_{\text{Cs}}} $ combination has a large and negative scattering length of $ a(\uparrow_{\text{Na}} \downarrow_{\text{Cs}}) = -693.8a_0 $ (interaction shift $\approx$ binding?)~\cite{Hood2019}. In addition to the increased atomic coupling, $ \Omega_a $, with the $\ket{\uparrow_{\text{Na}} \downarrow_{\text{Cs}}}$ hyperfine combination, coupled channel calculations show that the most weakly bound molecular state that is predominantly in this spin combination also has reduced coupling, $ \Omega_m $, with the excited state when compared with the $\ket{\uparrow_{\text{Na}}\uparrow_{\text{Cs}}}$ and $\ket{\downarrow_{\text{Na}}\downarrow_{\text{Cs}}} $ bound states. Therefore, using an initial $\ket{\uparrow_{\text{Na}} \downarrow_{\text{Cs}}}$ hyperfine combination results in a $ \Omega_a/\Omega_m$ ratio of about 0.05 instead of a ratio of about 0.003 with the other combinations.

@@

Thus, we choose the $\ket{\uparrow_{\text{Na}} \downarrow_{\text{Cs}}}$ spin combination as our initial state and drive to the first bound state for the $\ket{\uparrow_{\text{Na}} \downarrow_{\text{Cs}}}$ spin combination. %(We might want to mention that those ratios are for 80 kHz spherical trap if we want to give more details about the coupled channel calculation anywhere...)

@@

%% Preparation
To perform the Raman transfer, we use our apparatus described in our previous work~\cite{Liu2019}. Our experiment begins by stochastically loading a single ${}^{23}\mathrm{Na}$ atom and a single ${}^{133}\mathrm{Cs}$ atom into an optical tweezer from a dual-species MOT\todo{cite na loading paper} into separate optical tweezers. The atoms are initially imaged to distinguish between loading of two atoms, one atom (Na or Cs), or no atom in order to perform post selection. We then perform simultaneous Raman sideband cooling (RSC) to cool both atoms into the 3-dimensional motional ground state of their optical tweezers. After RSC, the Na tweezer is moved by sweeping the frequency on an acoustical optical beam deflector (AOBD) to overlap with the Cs tweezer before smoothly ramping off, so that the Na and Cs atoms are merged into the same tweezer~\cite{Liu2019}. The spin states for the Na and Cs atoms after RSC and during the merge process are $\ket{\uparrow_{\text{Na}}\uparrow_{\text{Cs}}} $. This states combination has a low scattering length, which allows the two atoms to be merged into the same tweezer with minimum pertubation on each other and thus they remain in the motional ground state after the merge.

After preparing the Na and Cs atoms in the same tweezer in a single quantum state, we need to drive the atoms into the large scattering length $\ket{\uparrow_{\text{Na}} \downarrow_{\text{Cs}}}$ hyperfine combination. To do this, we perform a spin flip taking into account the interaction shift~\cite{Hood2019} using a Cs Raman transition to drive the Cs atom into the $\ket{\downarrow_{\text{Cs}}}$ state. The new spin state combination has a larger scattering length of $-693.8 a_0$ which generates a interaction shift of $-30.7 kHz$ in the tweezer. This interaction shift is larger than the differential axial trapping frequency between Na and Cs atoms, which decouples the relative and center of mass motional state and improves the robustness of our preparation of the relative motion ground state.

@@

%% Transfer scheme
After the atoms are prepared in the $\ket{\uparrow_{\text{Na}}\uparrow_{\text{Cs}}} $ hyperfine combination, we then perform the Raman transfer. The pulse sequence for this step is shown in Fig.~\ref{f-raman}B. Instead of adding another beam to drive the Raman transition on the atoms in the tweezer, we use the tweezer itself to achieve this goal. In particular, we turn on two co-propagating frequencies in the tweezer during the Raman pulse. The dual use of the tweezer beam ensures that there is not any undesired laser frequency that can interfere with the Raman transition, and also allows us to maximize the Raman Rabi frequency and minimize the transfer time. After the total tweezer power is set to the desired value, we smoothly ramp down the power of one frequency in the tweezer while simultaneously ramping up the power of a different frequency so that the total tweezer power remains unchanged. Both frequencies are kept on for a variable length of time before the process is reversed and we return to having a single frequency in the tweezer.
In addition to reducing the number of laser beams during the Raman transition,
we also found the spectral purity of the laser to be critical for achieving a higher
transfer efficiency. The tweezer and Raman beams are generated by amplifying a $1037 \mathrm{nm}$
external cavity diode laser (ECDL) with a fiber amplifier,
which produces a broad band amplified spontaneous emission (ASE)
in addition to the desired frequency. This increases the scattering rate due to coupling to
other excited states.
We use a Bragg grating with a line width (FWHM) of $50 \mathrm{GHz}$ to clean up the
laser spectrum and found it reduces the scattering rate by at least a factor of $2$
for a particular single photon detuning.

@@

The ratio of molecule scattering rate to the Rabi frequency is larger than the theory prediction
by more than a factor of $10$.
Based on the calculation above, if this comes from the coupling to the $v'=0$ excited state,
it can be either due to a high ratio of $\Omega_m / \Omega_a$ or a large $\Gamma_e$.
Additionally, coupling to other excited states can also add an offset to both the Raman
Rabi frequency and the scattering rate which can affect the scattering rate
to Rabi frequency ratio.

@@

First we look at the change in resonance frequency.
As a function of the tweezer power, we observe a linear dependency on the resonance frequency
caused by the differential light shift between the atomic and molecular state (Fig.~\ref{f-det}A).
When we vary the tweezer frequency around the $v'=0$ excited state,
we can further observe a $1/\delta$ component and a constant component
in the experimentally explored region.
The background is caused by coupling to other excited states that are further away in energy.
The $1/\Delta$ component, however, is predominantly due to the coupling between
the molecular state and the $v'=0$ excited state.
From this measurement, we can calculate a matrix element between the molecular state and
the excited state, $\Omega_m$, of $2\pi\times36.162(20) \mathrm{MHz}/\sqrt{\mathrm{mW}}$
or $2\pi\times140.056(78) \mathrm{MHz}$ for the $15 \mathrm{mW}$ tweezer power used above.
This number is consistent with the value of
$2\pi\times27 \mathrm{MHz}/\sqrt{\mathrm{mW}}$ calculated from theory. \todo{ref/sm theory}
\todo{make sure theory part mentions $\Omega_{down}\gg\Omega_{up}$,
  also $\Omega$ vs $\Omega'$ for the single leg vs cross coupling number.}

In order to calculate the matrix element ratio, we now need to extract the matrix element between the atomic state and the excited molecular state, $ \Omega_a $. We do this by measuring the dependencies of the Raman Rabi frequency, which depends on both $\Omega_m$ and $\Omega_a$.
The Raman Rabi frequency shows a non-linear dependency on the tweezer power due to the change
in the atomic wavefunction caused by the change in confinement (Fig.~\ref{f-det}B).
The atomic matrix element, $\Omega_a$,
is proportional to the the short range atomic wavefunction amplitude,
which scales as $P^{0.375}$ for weakly interacting particles.
However, due to the strong interaction between the two atoms, this approximation breaks down.
Instead, theory calculation shows that the scaling is very well approximated by $P^{0.29}$
within the range of confinement in our experiment.
Combined with the intensity factor, the Raman Rabi frequency should scale with $P^{1.29}$,
which agrees with our experimental result.
Similar to the light shift, there is also an offset and
a $v'=0$ component in the Raman Rabi frequency that scales as $1/\Delta$.
The $v'=0$ component of the Raman Rabi frequency is
$2\pi\times161.8(22) \mathrm{Hz\cdot mW^{-1.29}}$,
or $2\pi \times 5.324(73)\mathrm{kHz}$ at $15 \mathrm{mW}$ tweezer power.
Together with the $\Omega_m$ measured above, the up leg Rabi frequency is
$2\pi \times 11.53(16)\mathrm{MHz}$.
This gives a Rabi frequency, and therefore matrix element, ratio of $12.14(16)$,
which is in fact better than the theory prediction of $23.7$
and should not cause the scattering from the $v'=0$ state to be higher than expected.

Unfortunately, the offset in the Raman Rabi frequency fit cancels
the Rabi frequency for red detuning Raman transition and reduces it by about $30\%$
at the current detuning. However, this difference is not enough to explain
the difference we observed in the experiment.
The same offset will increase the Rabi frequency for blue detuning
but we have observed additional excited states at slightly higher frequencies
which prevent the blue side of the transition to be usable for the Raman transition.

\begin{figure*}
  \includegraphics[height=4.5cm]{fig4.pdf}
  \caption{Raman transition parameters as a function of tweezer and Raman power and detuning.
    (A) The light shift of the Raman resonance scales as $P_{tweezer}$
    and follows $1/\Delta$ with an offset.
    The fit also includes a small term that is proportional to $P_{tweezer}^2$
    which is caused by the effective magnetic field generated by the tweezer which is
    perpendicular to the real magnetic field.
    (B) Raman Rabi frequency scales as $P_{tweezer}^{1.29}$ and follows $1/\Delta$ with an offset.
    From these results we can confirm the theory prediction of
    the atom-molecule matrix element ratio.
    (C) Atomic scattering rate scales as $P_{tweezer}^{2.58}$,
    this is consistent with a two photon scattering process.
    We have not measured a clear dependency of the loss rate on the tweezer detuning.
    \label{f-det}}
\end{figure*}

Based on our previous measurements of the excited state using photoassociation (PA) spectroscopy,
the natural linewidth of the $v'=0$ excited state is no larger than $20 \mathrm{MHz}$.
This suggests that the excited state linewidth should not cause a stronger than expected
scattering from $v'=0$ state either.
